Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-06-08 manuscript.tex
Update 'aims' with a clarification [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/f0b634e60b036c18080d89c63034379371acaf83.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/f0b634e60b036c18080d89c63034379371acaf83/checks
https://github.com/habi/acinar-analysis-manuscript/runs/918746106

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...7424b13151dd7ab8577f9a0021eb0408c29c1df5}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/7424b13151dd7ab8577f9a0021eb0408c29c1df5/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/7424b13151dd7ab8577f9a0021eb0408c29c1df5}{habi/acinar-analysis-manuscript@7424b13}
on June 4, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(7424b13)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(7424b13)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

While the global volume of the acini is well known and studied, only little is known about the range of the volume of individual acini throughout lung development.
We developed the hereby presented method to analyze large amounts of acini over the course of postnatal lung development in a time-efficient manner since no data on large amounts of acini is available up to now.
Our aim was to understand the size distribution of the acini during lung development including the contribution of the alveoli.
The observed range \emph{de}creased during postnatal lung development by a factor of 6--7, which represents a completely unexpected result.
The obtained data are essential for further investigations, like the influence of the size of the acini on ventilation or gas-washout, respectively.
E.g., we are currently using our computational fluid dynamics model to simulate exactly this influence (own unpublished results and {[}\protect\hyperlink{ref-eb0gk6VO}{13}{]}).

@@

JS conceived the project.
DH, SB and JS performed the tomographic data acquisition.
DH segmented the acini.
EY and DH stereologically analyzed the acini.
DH, ST, TC and JS analyzed the data.
DH wrote the manuscript and generated all the figures.
ST and JS contributed to writing, all authors proof-read the manuscript.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...f0b634e60b036c18080d89c63034379371acaf83}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/f0b634e60b036c18080d89c63034379371acaf83/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/f0b634e60b036c18080d89c63034379371acaf83}{habi/acinar-analysis-manuscript@f0b634e}
on June 8, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(f0b634e)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(f0b634e)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

While the global volume of the acini is well known and studied, only little is known about the range of the volume of individual acini throughout lung development.
We developed the hereby presented method to analyze large amounts of acini over the course of postnatal lung development in a time-efficient manner since no data on large amounts of acini is available up to now.
Our aim was to understand the size distribution of the acini during lung development including the contribution of the rather irregular shape of the alveoli.
The observed range \emph{de}creased during postnatal lung development by a factor of 6--7, which represents a completely unexpected result.
The obtained data are essential for further investigations, like the influence of the size of the acini on ventilation or gas-washout, or the influence of the irregular alveolar shape on partivle deposition inside individual acini, respectively.
E.g., we are currently using our computational fluid dynamics model to simulate exactly this influence (own unpublished results and {[}\protect\hyperlink{ref-eb0gk6VO}{13}{]}).

@@

JS conceived the project.
DH, SB and JS performed the tomographic data acquisition.
DH segmented the acini.
EY and DH stereologically analyzed the acini.
DH, ST, TC and JS analyzed the data.
DH wrote the manuscript and generated all the figures.
ST and JS contributed to writing.
All authors proof-read the manuscript.
